UGrade: Autograder for Competitive Programming Using Contestant PC as Worker

### 2019-11-02 src/paper.tex
clarify why domjudge only uses 2 workers

The grading performance between UGrade and DOMJudge was compared. DOMJudge was choosen as the comparison because it is open source and has been used in many competitive programming competitions. UGrade and DOMJudge were deployed in a computer with the same specification. Then fifteen computers were deployed to simulating the contestant actions. For DOMJudge, two more computers were deployed to work as the autograder worker. For UGrade, the fifteen computers worked as workers.

>>>>

The grading performance between UGrade and DOMJudge was compared. DOMJudge was chosen as the comparison because it is open source and has been used in many competitive programming competitions. UGrade and DOMJudge were deployed on a computer with the same specification. Then fifteen computers were deployed to simulating the contestant actions. For DOMJudge, two more computers were deployed to work as the autograder worker. The number of two were chosen based on the Arkavidia competition where there were six workers for one hundred contestants, so approximately one worker is enough to handle fifteen contestants. For UGrade, the contestants act as a worker so there are fifteen computers worked as workers.
